---
title: "Predict ER"
author: "Bryan Routledge"
date: "8/18/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Load the data ... 
This also makes the "target" Return and St.dev for the next 12 months

```{r }
setwd("/Users/rout/Desktop/Dropbox/2019m6-46892-MSBA-fin/RCode/Assign6") 
source("Main.A6.R")

```

# Make some Forecasts and Some Plots 
This is in *RunsForClass.R* 

First -- Lets preduct some Expected Returns (12 month horison)

My parameter *Interesting* is selecting a lambda regularizer parameter.
I did this by picking from the st.dev of the forecast.  If you set
the regularizer to really big, the st.dev of the forecast goes to zero.
I am using my *prior* that the variation in E[R] should not be zero and not too big

```{r echo=TRUE}
ER<-"E[R| date t]"


z<- Forecast(
		D=Data,
		what=c("Market"),
		use=c("CONSTANT","DPratio"),
		Interesting=c(0.5)   
		)
p<-Plot.Forecast(z,clip=c(0.01,.2),target=ER,title="DP Ratio")
print(p)

z<- Forecast(
		D=Data,
		what=c("Market",Use.Industries),
		use=c("CONSTANT","DPratio"),
		Interesting=c(0.5)   
		)
p<-Plot.Forecast(z,clip=c(0.01,.2),target=ER,title="DP Ratio")
print(p)


z<- Forecast(
		D=Data,
		what=c("Market",Use.Industries),
		use=c("CONSTANT","PDratio","gaip","recession","CreditSpread","TermSpreadL","unrate"),
		Interesting=c(0.05)
		)

p<-Plot.Forecast(z,clip=c(0.01,.2),target=ER,title="DP Ratio,int rate, unemployment")		
print(p)

z<- Forecast(
		D=Data,
		what=c("Market",Use.Industries),
		use=c("inflation","unrate"), # Growth IP 
		Interesting=c(0.05)
		)
p<-Plot.Forecast(z,clip=c(0.01,.2),target=ER,title="inflation,unemployment")
print(p)

z<- Forecast(
		D=Data,
		what=c("Market",Use.Industries),
		use=c("CONSTANT","recession"), # Growth IP 
		Interesting=c(0.05)
		)
p<-Plot.Forecast(z,clip=c(0.01,.2),target=ER,title="Just nber recession {1,0}")
print(p)


z<- Forecast(
		D=Data,
		what=c("Market",Use.Industries),
		use=c("FEDFUNDS","TermSpreadS","TermSpreadL", "CreditSpread"), # Growth IP 
		Interesting=c(0.05)
		)
p<-Plot.Forecast(z,clip=c(0.01,.2),target=ER,title="just interest rates")
print(p)


z<- Forecast(
		D=Data,
		what=c("Market",Use.Industries),
		use=c("gaip","gacr"), # Growth IP 
		Interesting=c(0.1)
		)
p<-Plot.Forecast(z,clip=c(0.01,.2),target=ER,title="recent growth")
print(p)

z<- Forecast(
		D=Data,
		what=c("Market",Use.Industries),
		use=colnames(P[,grepl("ga",colnames(P))]), # Growth IP 
		Interesting=c(0.01)
		)
p<-Plot.Forecast(z,clip=c(0.01,.2),target=ER,title="recent growth (many)")	
print(p)

z<- Forecast(
		D=Data,
		what=c("Market",Use.Industries),
		use=colnames(P[,-c(1:3)]), # EVERYTHING
		Interesting=c(0.01)
		)
p<-Plot.Forecast(z,clip=c(0.01,.2),target=ER,title="Everything")		
print(p)


```

# Predict Volatility

This is predicting the volatility over the next 12 months.  I calcualted this as V= sum(eR^2) - (average eR)^2. then sigma=sqrt(V).  there are other ways to define this.  

In general volatility is more predictible

```{r echo=TRUE}

VR<-"sigma[R| date t]"

z<- Forecast(
		D=Data,
		what=c("Market"),
		use=c("CONSTANT","DPratio"),
		Interesting=c(0.1,0.25,0.5,0.75,.9),
		LHS="V"
		)
Plot.Forecast(z,clip=c(0.01,.25),target=VR,title="DP Ratio (several lambda)",h=sqrt(12),highlight="")


z<- Forecast(
		D=Data,
		what=c("Market",Use.Industries),
		use=c("CONSTANT","DPratio"),
		Interesting=c(0.5),
		LHS="V"
		)
Plot.Forecast(z,clip=c(0.01,.25),target=VR,title="DP Ratio",h=sqrt(12))

z<- Forecast(
		D=Data,
		what=c("Market",Use.Industries),
		use=c("CONSTANT","recession"), # Growth IP 
		Interesting=c(0.5),
		LHS="V"
		)
Plot.Forecast(z,clip=c(0.01,.25),target=VR,title="recession",h=sqrt(12))

z<- Forecast(
		D=Data,
		what=c("Market","Rtail", "Util",  "Oil"),
		use=c("CONSTANT","recession"), # Growth IP 
		Interesting=c(0.5),
		LHS="V"
		)
Plot.Forecast(z,clip=c(0.01,.25),target=VR,title="recession",h=sqrt(12))


z<- Forecast(
		D=Data,
		what=c("Market",Use.Industries),
		use=colnames(P[,-c(1:3)]), # EVERYTHING
		Interesting=c(0.01),
		LHS="V"
		)
Plot.Forecast(z,clip=c(0.01,.25),target=VR,title="Everything",h=sqrt(12))
	

```
